---
title: "Getting Started with LOLA"
author: "Nathan Sheffield"
date: "`r Sys.Date()`"
vignette: >
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteIndexEntry{Getting Started with MSPC}
output: knitr:::html_vignette
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting started with MSPC
  
In this vignette, you'll use small example datasets that come with the MSPC package to get a first look at the most common functions in a MSPC workflow.

You need to read peak files as GRanges objects to easily rich functions from Bioconductor software. Here is the quick overview to fire up MSPC Packages

1. hit readPeakFile function which allow you to load all peaks files in R as S4 objects. 
2. remove all background noise is needed before peak overlapping meta analysis. We define efficient framework aim to remove all background peaks (a.k.a, noise peak) which facilitate the whole analysing more efficiently. We set up threshold value for peaks pvalue, where extremely weekly enriched peaks must be filtered out, while rest of the peaks will participate further meta analysis process. 
3. In our specificatin, we need to process peak interval element wise and to find its overlapped interval from all peaks files simultanously. We did implement quite efficient function to do this job. Apparently, vectorization is quite efficient way to prcess thousands of peaks reads. 

Let's load peak dataset with `readPeakFile`. Here's a small example that comes with MSPC. :


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
